alternativeRSA

### 2016-01-20 models/RSA_alternativeCostFormulation.Rmd
updated empty costs, re-outputed allModelRuns WITH salience costs

Data set-up
```{r}
# All scales studied
# ------------------
scales <- c("good_excellent",
            "liked_loved",
            "palatable_delicious",
            "memorable_unforgettable",
            "some_all")
# Priors
# ------
unifPriors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
empPriors = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/emp_priors.csv")
yelpPriors <- data.frame(stars=1:5,
                         prior.p =
                           c(0.090190981, 0.105689431, 0.162783722, 0.304569543, 0.336766323))
# Cost / rewards
# --------------
emptyCosts5 <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
                            cost = rep(0.0, 5), stringsAsFactors = FALSE)
emptyCosts4 <- data.frame(degree = c("low2", "low1","hi2", "hi1"),
                            cost = rep(0.0, 4), stringsAsFactors = FALSE)
emptyCosts2 <- data.frame(degree = c("low", "hi"),
                            cost = rep(0.0, 2), stringsAsFactors = FALSE)
salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
salienceCosts4 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences4.csv")
salienceCosts2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences2.csv")
# normNegSalienceCosts <- function(saliences) {
#   for (s in scales) {
#     saliences[saliences$scale == s, ]$cost <-
#       -1 * normedVec(saliences[saliences$scale == s, ]$cost)
#   }
#   saliences
# }
# salience <- c(0.22, 0.08, 0.05, 1, 1)
# saliencePriors <- data.frame(stars=1:5, prior.p = (salience / sum(salience)))
# salienceCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
#                             cost = -1 * (salience / sum(salience)), stringsAsFactors = FALSE)

@@

############# NEW SALIENCES 1/20/16 #########
salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
NUM_ALTERNATIVES_E9 <- 180
normNegSalienceCosts <- function(saliences) {
  saliences$cost <- c(rep(NA, nrow(saliences)))
  for (s in scales) {
    saliences[saliences$scale == s, ]$cost <-
      (-1 * saliences[saliences$scale == s, ]$newCount) / NUM_ALTERNATIVES_E9
    saliences[saliences$scale == s, ]$cost <-
      -1 * normedVec(saliences[saliences$scale == s, ]$cost)
  }
  saliences[, c("scale", "degree", "cost")]
}
############# NEW SALIENCES 1/20/16 #########

@@

completeModelRun <- function(speaker, listener, priors, costs, numAlts) {
  results <- list() ## Will return this

  newCosts <- normNegSalienceCosts(costs)
  data <- left_join(speaker, newCosts) %>%
    left_join(., priors) %>%
    rowwise %>%
    select(scale, degree, stars, speaker.p, prior.p, cost) %>%
    group_by(scale)

@@

Entailment / Neg alts / Symmetric scale
```{r}
symmetricScalerun <- completeModelRun(speakerL12, listener, unifPriors, salienceCosts5, numAlts = 5)
symmetricScalerun[[4]]
negAltsRun <- completeModelRun(speakerL10, listener, unifPriors, salienceCosts4, numAlts = 4)
negAltsRun[[4]]
entailmentRun <- completeModelRun(speakerL08, listener, unifPriors, salienceCosts2, numAlts = 2)
entailmentRun[[4]]

######WORKING HERE!!!!!!

@@

# write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
```

>>>>

Data set-up
```{r}
# All scales studied
# ------------------
scales <- c("good_excellent",
            "liked_loved",
            "palatable_delicious",
            "memorable_unforgettable",
            "some_all")
# Priors
# ------
unifPriors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
empPriors = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/emp_priors.csv")
yelpPriors <- data.frame(stars=1:5,
                         prior.p =
                           c(0.090190981, 0.105689431, 0.162783722, 0.304569543, 0.336766323))
# Cost / rewards
# --------------
emptyCosts5 <- data.frame(scale = c(rep("good_excellent", 5),
                                    rep("liked_loved", 5),
                                    rep("memorable_unforgettable", 5),
                                    rep("palatable_delicious", 5),
                                    rep("some_all", 5)),
                          degree = rep(c("hi1", "hi2", "mid", "low1", "low2"), 5),
                          newCount = rep(0.0, 25),
                          stringsAsFactors = FALSE)
emptyCosts4 <- data.frame(scale = c(rep("good_excellent", 4),
                                    rep("liked_loved", 4),
                                    rep("memorable_unforgettable", 4),
                                    rep("palatable_delicious", 4),
                                    rep("some_all", 4)),
                          degree = rep(c("hi1", "hi2", "low1", "low2"), 5),
                          newCount = rep(0.0, 20),
                          stringsAsFactors = FALSE)
emptyCosts2 <- data.frame(scale = c(rep("good_excellent", 2),
                                    rep("liked_loved", 2),
                                    rep("memorable_unforgettable", 2),
                                    rep("palatable_delicious", 2),
                                    rep("some_all", 2)),
                          degree = rep(c("hi", "low"), 5),
                          newCount = rep(0.0, 10),
                          stringsAsFactors = FALSE)

# degree = c("low2", "low1", "mid", "hi2", "hi1"),
#                             newCount = rep(0.0, 5), stringsAsFactors = FALSE)
emptyCosts4 <- data.frame(degree = c("low2", "low1","hi2", "hi1"),
                            newCount = rep(0.0, 4), stringsAsFactors = FALSE)
emptyCosts2 <- data.frame(degree = c("low", "hi"),
                            newCount = rep(0.0, 2), stringsAsFactors = FALSE)
salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
salienceCosts4 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences4.csv")
salienceCosts2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences2.csv")
# normNegSalienceCosts <- function(saliences) {
#   for (s in scales) {
#     saliences[saliences$scale == s, ]$cost <-
#       -1 * normedVec(saliences[saliences$scale == s, ]$cost)
#   }
#   saliences
# }
# salience <- c(0.22, 0.08, 0.05, 1, 1)
# saliencePriors <- data.frame(stars=1:5, prior.p = (salience / sum(salience)))
# salienceCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
#                             cost = -1 * (salience / sum(salience)), stringsAsFactors = FALSE)

@@

############# NEW SALIENCES 1/20/16 #########
salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
NUM_ALTERNATIVES_E9 <- 180
normNegSalienceCosts <- function(saliences) {
  # Add cost column
  saliences$cost <- c(rep(0, nrow(saliences)))

  # Check if we've passed emptyCost
  if (all(saliences$newCount == 0)) return(saliences[, c("scale", "degree", "cost")])

  for (s in scales) {
    saliences[saliences$scale == s, ]$cost <-
      (-1 * saliences[saliences$scale == s, ]$newCount) / NUM_ALTERNATIVES_E9
    saliences[saliences$scale == s, ]$cost <-
      -1 * normedVec(saliences[saliences$scale == s, ]$cost)
  }
  saliences[, c("scale", "degree", "cost")]
}
############# NEW SALIENCES 1/20/16 #########

@@

completeModelRun <- function(speaker, listener, priors, costs, numAlts) {
  results <- list() ## Will return this
  newCosts <- normNegSalienceCosts(costs)

  data <- left_join(speaker, newCosts) %>%
    left_join(., priors) %>%
    rowwise %>%
    select(scale, degree, stars, speaker.p, prior.p, cost) %>%
    group_by(scale)

@@

Run complte analyses and output to csv
```{r}
# Run analyses
symmetricScalerun <- completeModelRun(speakerL12, listener, unifPriors, salienceCosts5, numAlts = 5)
symmetricScalerun[[4]]
negAltsRun <- completeModelRun(speakerL10, listener, unifPriors, salienceCosts4, numAlts = 4)
negAltsRun[[4]]
entailmentRun <- completeModelRun(speakerL08, listener, unifPriors, salienceCosts2, numAlts = 2)
entailmentRun[[4]]

@@

#write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
```
